---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

# tar-render-book-demo

The goal of tar-render-book-demo is to provide a preview of creating a bookdown book using a [targets](https://github.com/ropensci/targets) pipeline.

This project was created with the template book by calling `bookdown::create_bs4_book(path = "demo-book")`. I added a section to the file `demo-book/01-intro.Rmd` to use the `data` target created as part of the default `_targets.R` file generated with `targets::tar_script()`. I also modified the `demo-book/index.Rmd` file to write the 'packages.bib' to `demo-book/packages.bib`.

After running the pipeline, any time we update or modify a file in the "demo-book" folder, the target `demo_book` will become outdated.

## `_targets.R` File

```{r read-script, echo = FALSE}
cat(
  readLines("_targets.R"),
  sep = "\n"
)
```

## Run and Visualize Pipeline

```{r show-visnetwork, echo = TRUE}
targets::tar_make()
targets::tar_visnetwork(targets_only = TRUE)
```

## Invalidate Pipeline

We can invalidate the pipeline by modifying any of the files in the "demo-book" directory. One easy way is just to add a new line to a file.

```{r overwrite-file}
writeLines(
  text = c(
    readLines("demo-book/01-intro.Rmd"), 
    "new line here!"
    ),
  con = "demo-book/01-intro.Rmd"
  )
```

```{r show-visnetwork-outdates}
targets::tar_visnetwork(targets_only = TRUE)
```

